---
title: "Participation in CFTC Rulemaking"
subtitle: "Frequency"
output:
    bookdown::html_document2:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
      number_sections: false
---

```{r options, include=FALSE}
library(marginaleffects)
library(fixest)

# rmarkdown::render("docs/participation.Rmd")
source(here::here("code", "setup.R"))

## Change defaults for R chunks
knitr::opts_chunk$set(cache = TRUE,
                      fig.path = "figs/",
                      #fig.retina = 3, #6, #FIXME for publication-quality images 
                      fig.height = 3,
                      fig.width = 7)

#Steve specific code - this is the secret sauce to make it work on my mac.  Why is this the key?  
#setwd("/Users/stevenrashin/Dropbox/FINREGRULEMAKE2/finreg/")
#here::i_am("code/setup.R")
```


# Data

From judgelord.github.io/finreg/participation.html


```{r}
load(here::here("data", "commenter_assets.Rdata"))
d <- commenter_assets |> 
  filter(comment_agency == "CFTC") 

#FIXME WE SHOULD NOT NEED THIS 
# load IRS data with c3-c6 variable (this is large)
# load(here::here("data", "IRS990-2012-2021.RData"))
# 
# IRS990_2012_2021 %<>% distinct(EIN, ORGANIZATION, SUBSECTION, .keep_all = T)
```

---

# Frequency of participation among organizations that commented

Among commenting organizations, how many rules did each comment on?

WARNING: THIS IS A PROBLEMATIC MEAURE BECAUSE MARKET CAP AND NGO ASSETS ARE NOT AT ALL THE SAME 

```{r asset-counts, fig.width=4, fig.height= 2, out.width= "50%"}

asset_counts <- d %>% 
  mutate(assets = org_resources) %>% 
  filter(assets > 10) %>%
  distinct(org_name, docket_id, assets) %>% 
  count(org_name, assets) %>% 
  filter(!is.na(assets)) %>% 
  mutate(nnp = quantile(n, probs = .9),
         assets_m = assets /1000000,
         assets_b = assets_m / 1000,
         onepercent = ifelse(n > nnp, "Top 10%", "Bottom 90%"),
         five = ifelse(n < 5, "<5 Rules", "5 or More Rules"),
         top = n > nnp)

rules_t <- t.test(asset_counts %>% filter(top) %>% pull(assets),
                  asset_counts %>% filter(!top) %>% pull(assets),)

rules_t

asset_counts %>% 
  ggplot() + 
  aes(x = n,  fill = onepercent) + 
  geom_bar() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Banks and Non-profits" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       y = "Number of Organizations",
       fill = "Frequency of\nCommenting",
       x = "Dodd-Frank Rules per Organization") #+ scale_y_log10()


asset_counts %>% 
  ggplot() + 
  aes(x = assets_m, fill = five) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Banks and Non-profits" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       y = "", 
       x = "Assets (Millions)")+
  scale_fill_viridis_d(begin = .3, end = .9) +  
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())

  

asset_counts %>% 
  ggplot() + 
  aes(x = assets_m, fill = onepercent) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Banks and Non-profits" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       y = "", 
       x = "Assets (Millions)")+
  scale_fill_viridis_d(begin = .3, end = .9) +  
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())




m_asset_count <- lm(n ~ assets_b, data = asset_counts)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Number of Rules",
)

attr(rows, 'position') <- c(0)

modelsummary(m_asset_count)
```


For every additional 10 billion in assets, an organization comments on about `r round(m_asset_count$coefficients[2]* 10,0) ` additional rules. 

---

## Among nonprofits that commented on a Dodd-Frank rule

```{r nonprofit-rules, fig.width=4, fig.height= 2, out.width= "50%"}
# ein_subsection <- IRS990_2012_2021 %>%
#   dplyr::select(EIN,SUBSECTION) %>%
#   mutate(ein = as.double(EIN)) %>%
#   dplyr::select(-EIN) %>%
#   distinct() #%>%
#   #group_by(EIN) %>% tally() %>% arrange(desc(n))


asset_counts <- d %>% 
  filter(assets > 10) %>%
  distinct(org_name, docket_id, assets, .keep_all = T) %>% 
  #left_join(ein_subsection) %>% ### ADDED SUBSECTION HERE ## NOTE INCASE CODE GOES ROGUE
  count(org_name, assets, ein, SUBSECTION) %>% # length stays at 6283 when ein added, so no change here!
  filter(!is.na(assets)) %>% 
  mutate(nnp = quantile(n, probs = .9),
         assets_t = assets / 1000,
         assets_m = assets_t /1000,
         assets_b = assets_m / 1000,
         onepercent = ifelse(n > nnp, "Top 10%", "Bottom 90%"),
         five = ifelse(n < 5, "<5 Rules", "5 or More Rules"),
         top = n > nnp)

rules_nonprofits_t <- t.test(asset_counts %>% filter(top) %>% pull(assets),
                  asset_counts %>% filter(!top) %>% pull(assets),)

rules_ind_assoc_t <- t.test(asset_counts %>% filter(top) %>% pull(assets),
                  asset_counts %>% filter(!top) %>% pull(assets),)


rules_nonprofits_t 

asset_counts %>% 
  ggplot() + 
  aes(x = n, fill = onepercent) + 
  geom_bar() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Non-profits" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       y = "Number of Non-profits",
       fill = "Frequency of\nCommenting",
       x = "Number of Dodd-Frank Rules") # + scale_y_log10()

asset_counts %>% 
  ggplot() + 
  aes(x = assets_t, fill = five) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Non-profits" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
        fill = "Frequency of\nCommenting", y = "", x = "Assets (Thousands)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_nonprofits_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())
  

asset_counts %>% 
  ggplot() + 
  aes(x = assets_t, fill = onepercent) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Non-profits" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
        fill = "Frequency of\nCommenting", y = "", x = "Assets (Thousands)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_nonprofits_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())

### DO ABOVE BY SECTION OF IRS CODE TO SEPARATE OUT BUSINESS ASSNS
anova_group_means  <- aov(assets_t ~ sub_group_comment, data =   asset_counts %>%
    filter(assets > 10) %>%
    filter(SUBSECTION %in% c("03","06")) %>%
    mutate(
      sub_group_comment = c(paste(onepercent, SUBSECTION))
    ))

# library(rstatix)
# pwc <- asset_counts %>%
#     filter(assets > 10) %>%
#     filter(SUBSECTION %in% c("03","06")) %>%
#     mutate(
#       sub_group_comment = c(paste(onepercent, SUBSECTION))
#     ) %>%
#   rstatix::pairwise_t_test(assets_t ~ sub_group_comment, p.adjust.method = "bonferroni")
# pwc %>% View()
# None of the differences are statistically significant

## Top 10% against Bottom 90%
foc_top10_by_subsection <- asset_counts %>% 
  filter(SUBSECTION %in% c("03","06")) %>%
  mutate(
    onepercentsubsection = c(paste(onepercent, SUBSECTION))
  ) %>%
  ggplot() + 
  aes(x = assets_t, fill = onepercentsubsection) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Non-profits" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
        fill = "Frequency of\nCommenting by\nSubsection", y = "", x = "Assets (Thousands)",
       caption = str_c("ANOVA test of difference in group means, p = ", summary(anova_group_means)[[1]][1,5]  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())

# By 5 or more rules 
anova_group_means_five  <- aov(assets_t ~ five, data =   asset_counts %>%
    filter(SUBSECTION %in% c("03","06")) %>%
    mutate(
      five = c(paste(five, SUBSECTION))
    ))

foc_5more_by_subsection <- asset_counts %>% 
  filter(SUBSECTION %in% c("03","06")) %>%
  mutate(
    five = c(paste(five, SUBSECTION))
  ) %>%  
  ggplot() + 
  aes(x = assets_t, fill = five) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Non-profits" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
        fill = "Frequency of\nCommenting", y = "", x = "Assets (Thousands)",
       caption = str_c("ANOVA test of difference in group means, p = ", summary(anova_group_means_five)[[1]][1,5]  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())

foc_top10_by_subsection
foc_5more_by_subsection

m_nonprofit_count <- lm(n ~ assets_b, data = asset_counts)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Number of Dodd-Frank Rules",
)

attr(rows, 'position') <- c(0)

modelsummary(m_nonprofit_count)
```


For every additional 10 billion in assets, a nonprofit comments on about `r round(m_nonprofit_count$coefficients[2]* 10,1) ` additional rules. 

---

## Among industry associations that commented on a Dodd-Frank rule

```{r ind-assoc-rules, fig.width=4, fig.height= 2, out.width= "50%"}
#ind-assoc-rules commented on 
asset_counts <- d %>% 
  filter(assets > 10) %>%
  distinct(org_name, docket_id, assets, .keep_all = T) %>% 
  #left_join(ein_subsection) %>% ### ADDED SUBSECTION HERE ## NOTE INCASE CODE GOES ROGUE
  filter(SUBSECTION == "06") %>% 
  count(org_name, assets, ein) %>% # length stays at 6283 when ein added, so no change here!
  filter(!is.na(assets)) %>% 
  mutate(nnp = quantile(n, probs = .9),
         assets_t = assets / 1000,
         assets_m = assets_t /1000,
         assets_b = assets_m / 1000,
         onepercent = ifelse(n > nnp, "Top 10%", "Bottom 90%"),
         five = ifelse(n < 5, "<5 Rules", "5 or More Rules"),
         top = n > nnp)

rules_ind_assoc_t <- t.test(asset_counts %>% filter(top) %>% pull(assets),
                  asset_counts %>% filter(!top) %>% pull(assets),)

rules_ind_assoc_t <- t.test(asset_counts %>% filter(top) %>% pull(assets),
                  asset_counts %>% filter(!top) %>% pull(assets),)


rules_ind_assoc_t 

asset_counts %>% 
  ggplot() + 
  aes(x = n, fill = onepercent) + 
  geom_bar() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Industry Associations" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       y = "Number of Industry Associations",
       fill = "Frequency of\nCommenting",
       x = "Number of Dodd-Frank Rules") # + scale_y_log10()

asset_counts %>% 
  ggplot() + 
  aes(x = assets_t, fill = five) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Industry Associations" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
        fill = "Frequency of\nCommenting", y = "", x = "Assets (Thousands)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_ind_assoc_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())
  

asset_counts %>% 
  ggplot() + 
  aes(x = assets_t, fill = onepercent) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Industry Associations" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
        fill = "Frequency of\nCommenting", y = "", x = "Assets (Thousands)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_ind_assoc_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())
```



---

## Among  Banks that commented on a Dodd-Frank rule

```{r fdic-rules, fig.width=4,  fig.height= 2,out.width= "50%"}
asset_counts <- d %>% 
  mutate(assets = ASSET) %>% 
  filter(assets > 10) %>%
  distinct(org_name, docket_id, assets) %>% 
  count(org_name, assets) %>% 
  filter(!is.na(assets)) %>% 
  mutate(nnp = quantile(n, probs = .90),
         assets_t = assets /1000,
         assets_m = assets_t /1000,
         assets_b = assets_m / 1000,
         onepercent = ifelse(n > nnp, "Top 10%", "Bottom 90%"),
         five = ifelse(n < 5, "<5 Rules", "5 or More Rules"),
         top = n>nnp)

rules_fdic_t <- t.test(asset_counts %>% filter(top) %>% pull(assets),
                  asset_counts %>% filter(!top) %>% pull(assets),)

rules_fdic_t 

asset_counts %>% 
  ggplot() + 
  aes(x = n, fill = onepercent) + 
  geom_bar() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(y = "Number of Banks",
       title = "Banks" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       x = "Number of Dodd-Frank Rules") #+ scale_y_log10()
  
asset_counts %>% 
  ggplot() + 
  aes(x = assets_m, fill = five) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Banks" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       y = "", x = "Assets (Millions)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_fdic_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())

asset_counts %>% 
  ggplot() + 
  aes(x = assets_m, fill = onepercent) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Banks" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       y = "", x = "Assets (Millions)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_fdic_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())


m_fdic_count <- lm(n ~ assets_b, data = asset_counts)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Number of Dodd-Frank Rules"
  )

attr(rows, 'position') <- c(0)

modelsummary(list(m_fdic_count))
```


For every additional billion in assets, a bank comments on about `r round(m_fdic_count$coefficients[2]* 1,0) ` additional rules. 


---



## Among credit unions that commented on a Dodd-Frank rule

```{r creditunion-rules, fig.width=4,  fig.height= 2,out.width= "50%"}
asset_counts <- d %>% 
  mutate(assets = `Total Assets`) %>% # credit union call reports Total Assets
  filter(assets > -1, !is.na(assets)) %>%
  distinct(org_name, docket_id, assets) %>% 
  count(org_name, assets) %>% 
  mutate(nnp = quantile(n, probs = .5),
         assets_t = assets /1000,
         assets_m = assets_t /1000,
         assets_b = assets_m / 1000,
         onepercent = ifelse(n > nnp, "Top 50%", "Bottom 50%"),
         five = ifelse(n < 5, "<5 Rules", "5 or More Rules"),
         top = n>nnp)

rules_creditunion_t <- t.test(asset_counts %>% filter(top) %>% pull(assets),
                  asset_counts %>% filter(!top) %>% pull(assets),)

rules_creditunion_t

asset_counts %>% 
  ggplot() + 
  aes(x = n, fill = onepercent) + 
  geom_bar() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(y = "Number of Credit Unions",
       title = "Credit Unions" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       x = "Number of Dodd-Frank Rules") #+ scale_y_log10()
  
asset_counts %>% 
  ggplot() + 
  aes(x = assets_m, fill = five) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Credit Unions" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       y = "", x = "Assets (Millions)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_creditunion_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())

asset_counts %>% 
  ggplot() + 
  aes(x = assets_m, fill = onepercent) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Credit Unions" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       y = "", x = "Assets (Millions)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_creditunion_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())


m_creditunion_count <- lm(n ~ assets_b, data = asset_counts)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Number of Dodd-Frank Rules"
  )

attr(rows, 'position') <- c(0)

modelsummary(list(m_creditunion_count))
```


For every additional 10 billion in assets, a credit union comments on about `r round(m_creditunion_count$coefficients[2]* 10,0) ` additional rules. 


---


## Among publicly-traded companies that commented on a Dodd-Frank rule

```{r compustat-rules, fig.width=4, fig.height= 2, out.width= "50%"}
# compustat-rules
d %>% count(org_name, marketcap, sort = T) %>% drop_na(marketcap) %>%  kablebox()

d %>% count(org_name, organization, marketcap, sort = T) %>% drop_na(marketcap) %>%  kablebox()

d %>% filter(org_name == "alternative asset management acquisition") %>% dplyr::select(marketcap, organization,contains("name")) %>% kablebox()

# combine and count 
asset_counts <- d %>% 
  mutate(marketcap = marketcap2) %>% 
  filter(marketcap > 10) %>%
  distinct(org_name, docket_id, marketcap) %>% 
  count(org_name, marketcap) %>% 
  filter(!is.na(marketcap)) %>% 
  mutate(nnp = quantile(n, probs = .9),
         marketcap_t = marketcap /1000,
         marketcap_m = marketcap_t /1000,
         marketcap_b = marketcap_m / 1000,
         onepercent = ifelse(n > nnp, "Top 10%", "Bottom 90%"),
         five = ifelse(n < 5, "<5 Rules", "5 or More Rules"),
         top = n > nnp)

asset_counts %>% filter(n > 5) %>% count(marketcap, sort = T)
d %>% count(marketcap, sort = T)
#compustat %>% count(marketcap, sort = T)
d %>% filter(marketcap2 == 34297000000) %>% dplyr::select(marketcap, contains("name"), contains("cik"), contains("rssd")) %>% distinct() %>% kablebox()
#compustat %>% filter(marketcap2 == 34297000000) 

#FIXME we need to correct this to be a nonprofit, just dropping for now 
asset_counts %<>% filter(org_name != "alternative asset management acquisition")


rules_compustat_t <- t.test(asset_counts %>% filter(top) %>% pull(marketcap),
                  asset_counts %>% filter(!top) %>% pull(marketcap),)

rules_compustat_t 

asset_counts %>% 
  ggplot() + 
  aes(x = n, fill = onepercent) + 
  geom_bar() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(y = "Number of Companies",
       title = "Publicly-Traded Companies" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting",
       x = "Number of Dodd-Frank Rules") #+ scale_y_log10()
  
asset_counts %>% 
  filter(marketcap_b > .001) %>% 
  ggplot() + 
  aes(x = marketcap_b, fill = five) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Publicly-Traded Companies" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting", y = "", x = "Market Cap (Billions)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_compustat_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())


asset_counts %>% 
  ggplot() + 
  aes(x = marketcap_b, fill = onepercent) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Publicly-Traded Companies" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       fill = "Frequency of\nCommenting", y = "", x = "Market Cap (Billions)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_compustat_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())


m_compustat_count <- lm(n ~ marketcap_b, data = asset_counts)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Number of Dodd-Frank Rules"
  )

attr(rows, 'position') <- c(0)

modelsummary(list(m_compustat_count))
```


For every additional 100 billion in market cap, a company comments on about `r round(m_compustat_count$coefficients[2]* 100,0) ` additional rules. 

---

## Among campaign donors that commented on a Dodd-Frank rule

TODO: 
- [ ] Lobbying expendature
- [ ] Versions of PAC donations and lobbying expendature that replace NA with 0 (on the assumption that if they failed to match in CRP, they are not a PAC donor or registered with LDA)

```{r opensecrets-rules, fig.width=4, fig.height= 2, out.width= "50%"}
asset_counts <- d %>% 
  mutate(donations = `MeanContribAmount`) %>% 
   # mutate(donations = `MeanContribAmountPerYearContributed`) %>% 
  filter(donations > 10) %>%
  distinct(org_name, docket_id, donations) %>% 
  count(org_name, donations) %>% 
  filter(!is.na(donations)) %>% 
  mutate(nnp = quantile(n, probs = .9),
         donations_m = donations / 1000000,
         onepercent = ifelse(n > nnp, "Top 10%", "Bottom 90%"),
         five = ifelse(n < 5, "<5 Rules", "5 or More Rules"),
         top = n>nnp)

rules_pac_t <- t.test(asset_counts %>% filter(top) %>% pull(donations),
                  asset_counts %>% filter(!top) %>% pull(donations),)

rules_pac_t 


asset_counts %>% 
  ggplot() + 
  aes(x = n, fill = onepercent) + 
  geom_bar() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Campaign Donors" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
       y = "Number of Organizations",
        fill = "Frequency of\nCommenting",
       x = "Number of Dodd-Frank Rules") #+ scale_y_log10()
  

asset_counts %>% 
  ggplot() + 
  aes(x = donations_m, fill = five) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Campaign Donors" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
        fill = "Frequency of\nCommenting", 
       y = "", x = "PAC Donations (Thousands)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_pac_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())


asset_counts %>% 
  ggplot() + 
  aes(x = donations_m, fill = onepercent) + 
  geom_density(alpha = .5, color = NA) + 
  scale_x_log10() + 
  scale_fill_viridis_d(begin = .3, end = .9) +  
  labs(title = "Campaign Donors" %>% str_c(", CFTC, N = ", nrow(asset_counts) %>% prettyNum(big.mark = ",")),
        fill = "Frequency of\nCommenting", 
       y = "", x = "PAC Donations (Thousands)",
       caption = str_c("Welch t-test of difference in means, p = ", rules_pac_t$p.value  %>% round(20) %>% signif(1)))+
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.y = element_blank())


m_opensecrets_count <- lm(n ~ donations_m, data = asset_counts)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Number of Dodd-Frank Rules",
)

attr(rows, 'position') <- c(0)

modelsummary(m_opensecrets_count)
```


For every additional 10 million in Political Action Committee campaign donations, an organization comments on about `r round(m_opensecrets_count$coefficients[2]* 10,0) ` additional rules. 

---

## All

```{r all-rules}

models <- list(#`All` = m_asset_count, 
               `Non-profits` = m_nonprofit_count,
               `Credit Unions`= m_creditunion_count,
               `Public Companies` = m_compustat_count,
               `Banks` = m_fdic_count,
               `PAC Donors` = m_opensecrets_count)

rows <- tibble(
  term = c("Dependent Variable"),
  #`All` = "Number of Rules",
      `Non-profits` = "Number of Rules",
  `Credit Unions`= "Number of Rules",
  `Public Companies` = "Number of Rules",
  `Banks` = "Number of Rules",
    `PAC Donors` = "Number of Rules",
  )

attr(rows, 'position') <- c(0)


modelsummary(models)

save(models, rows, 
     file = here::here("models", "CFTC", "rules-by-assets.Rdata"))
```

---

## Comments per rule

### Percent of comments by each organization type on any one rule
```{r}
# comments 
# of the matched sample 
# 90% of credit union comments, half of the nonprofits, and 75% campaig
d %>% 
  mutate(docket_id = str_split(docket_id, ";")) %>% 
  unnest(docket_id) %>% 
    add_count(org_type2, name = "dataset_total") %>% 
  count(org_type2, docket_id, dataset_total, sort = T) %>%
  mutate(percent = percent( n / dataset_total , accuracy = 1)) %>% 
  kablebox()
```


### Percent of each organization type on any one rule

```{r}
# orgs (15% of nonprofits on payday loan rule, 30% of opensecrets)
d %>% 
 mutate(docket_id = str_split(docket_id, ";")) %>% 
  unnest(docket_id) %>% 
  # org rather than comment level counts now
  distinct(org_name, docket_id, org_type2) %>% 
  # total orgs of each type  in the dataset 
  add_count(org_type2, name = "dataset_total") %>% 
  # number of each org type by docket 
  count(org_type2, docket_id, `dataset_total`, sort = T) %>%
  mutate(percent = percent( n / dataset_total , accuracy = 1)) %>% 
  kablebox()
```

### Most Frequently Commenting Orgs
```{r}
# 
d %>% 
  # filter(comment_agency == "CFTC") %>% 
  # mutate(docket_id = comment_url %>% str_extract("CFTC-[0-9]*-[0-9]*")) %>% 
  count(best_match_name, org_type2, docket_id, sort = T) %>% kablebox()
```

      
