---
title: "Participation in CFPB Rulemaking"
subtitle: "Probability of Commenting on an CFPB Rule" 
output:
    bookdown::html_document2:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
      number_sections: false
---

(Those that "did not comment" may have commented on non-CFPB Dodd-Frank rules)

```{r options, include=FALSE}
library(marginaleffects)
library(fixest)

# rmarkdown::render("docs/participation.Rmd")
source(here::here("code", "setup.R"))

## Change defaults for R chunks
knitr::opts_chunk$set(cache = TRUE,
                      fig.path = "figs/",
                      #fig.retina = 3, #6, #FIXME for publication-quality images 
                      fig.height = 3,
                      fig.width = 7)

#Steve specific code - this is the secret sauce to make it work on my mac.  Why is this the key?  
#setwd("/Users/stevenrashin/Dropbox/FINREGRULEMAKE2/finreg/")
#here::i_am("code/setup.R")
```


# Data

From judgelord.github.io/finreg/participation.html


```{r}
load(here::here("data", "commenter_assets.Rdata"))
d <- commenter_assets |>
  filter(comment_agency == "CFPB") 

load(here::here("data", "nonprofit_resources_clean.Rdata"))

load(here::here("data", "fdic_resources_clean.Rdata"))
#https://banks.data.fdic.gov/docs/#/

load(here::here("data", "compustat_clean.Rdata"))

load(here::here("data", "opensecrets_clean.Rdata"))

load(here::here("data", "creditunions_clean.Rdata"))

#FIXME WE SHOULD NOT NEED THIS 
# load IRS data with c3-c6 variable (this is large)
#load(here::here("data", "IRS990-2012-2021.RData"))

#IRS990_2012_2021 %<>% distinct(EIN, ORGANIZATION, SUBSECTION, .keep_all = T)
```

---

# Probability of Commenting

These models have the prefix `mp_`. The dependent variable is the probability that the organization comments.

### Banks

SM = Comptroller of the Currency (CFPB). National Charter and a Fed member.

NM = Commercial Bank. The bank is supervised by the Federal Deposit Insurance Corporation (FDIC). State charter and Fed non-member

SB = Savings Bank. The bank is supervised by the Federal Deposit Insurance Corporation (FDIC). State Charter.

OI = Bank is an insured United States branch of a foreign chartered institution (IBA)

N = National Associations (Ommitted)

Assets in hundreds of millions

```{r cache=FALSE}
# FDIC_resources %>% filter(BKCLASS == "NM")


FDIC_resources %<>% mutate(
  Class = str_c(" ", BKCLASS) %>% as.factor() ,
  ASSETS_t = ASSET/1000,
  ASSETS_m = ASSETS_t/1000,
  ASSETS_b = ASSETS_m/1000) 

# make savings associations the ref category 
FDIC_resources$Class %<>% relevel(ref = " SA")
# %>% 
#   mutate(BKCLASS = BKCLASS %>% str_replace("^NM", "SBNM"))  %>% 
#   mutate(BKCLASS = BKCLASS %>% str_replace("^NM", "SBNM"))

unique(FDIC_resources$BKCLASS)
unique(FDIC_resources$Class)


```


```{r mp-FDIC, cache=FALSE, fig.height=2, fig.width=6}
#mpFDIC
mpFDICbillions <- glm(commented ~ ASSETS_b,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDIC <- glm(commented ~ ASSETS_b,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDIC_BKCLASSonly <- glm(commented ~ Class,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDIC_BKCLASS <- glm(commented ~ ASSETS_b + Class,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDICxBKCLASS <- glm(commented ~ ASSETS_b*Class,
           data = FDIC_resources, 
             family=binomial(link="logit"))


rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Comment",
  `2` = "Comment",  
  #`3` = "Comment"
)

attr(rows, 'position') <- c(0)

models <- list(mpFDIC,# mpFDIC_BKCLASSonly,
               mpFDIC_BKCLASS#,
               #mpFDICxBKCLASS
               )

# equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)

modelplot(models[1:2]) +
  labs(title  = "Banks",
x = "Change in Log Odds of Commenting",
caption = "Reference Category = Savings Associations") +
  theme(panel.grid.major.x =  element_blank(),
        panel.grid.major.y =  element_blank()) + 
  scale_color_viridis_d(end = .6)


save(models, rows, 
     file = here::here("models", "CFPB", "mpFDIC.Rdata"))
```


#### Predicted probabibility of commenting by bank type

```{r mp-FDIC-predict, fig.height=2.5, fig.width=6}
# mp-FDIC-predict

 # A data frame of values at which to estimate probabilities:
values <- FDIC_resources %>% 
  #filter(org_type == "Bank") %>% 
  tidyr::expand(ASSETS_b = seq(0,100,20),
                Class)#, org_type = "Bank") 

predicted <- marginaleffects::predictions(mpFDICxBKCLASS,
                         newdata = values) 

names(predicted)


# As a plot
p <- predicted %>% 
  mutate(Class = Class %>% 
           str_replace("NM", "Commercial bank") %>% 
      str_replace("SB", "Savings bank") %>% 
      str_replace("OI", "Foreign chartered institution") %>% 
      str_replace("N$", "National association") %>% 
        str_replace("SA", "Savings association") %>% 
        str_replace("SM", "State commercial bank")
    ) %>% 
  ggplot() + 
  aes(x = ASSETS_b, y = estimate, shape = Class, color = Class
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), 
                  alpha = .7,
                  position = position_dodge(width = 10) 
                  )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  #coord_flip() +
  labs(y = 'Probability of Commenting', 
       x = "Assets (Billions)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
  theme()+
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma")  

p 
```


```{r mp-FDIC2, cache=FALSE, fig.height=2, fig.width=6}
FDIC_resources %<>% mutate(Class2 = ifelse(
  str_detect(Class, "NM|SM"),
  "Commercial bank",
  "Non-commercial bank"
), 
ASSETS_b2 = ASSETS_b^2)

#mpFDIC
mpFDICbillions <- glm(commented ~ ASSETS_b,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDIC <- glm(commented ~ ASSETS_b,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDIC_BKCLASSonly <- glm(commented ~ Class2,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDIC_BKCLASS <- glm(commented ~ ASSETS_b + Class2,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDICxBKCLASS <- glm(commented ~ ASSETS_b*Class2,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDICxBKCLASSlog <- glm(commented ~ log(ASSETS_b)*Class2,
           data = FDIC_resources, 
             family=binomial(link="logit"))

mpFDICxBKCLASS2 <- glm(commented ~ ASSETS_b*Class2 + ASSETS_b2*Class2,
           data = FDIC_resources, 
             family=binomial(link="logit"))


rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Comment",
  `2` = "Comment",  
    `3` = "Comment",  
  `4` = "Comment"#,
  #  `5` = "Comment"
)

attr(rows, 'position') <- c(0)

models <- list(mpFDIC,# mpFDIC_BKCLASSonly,
               mpFDIC_BKCLASS,
               mpFDICxBKCLASS,
                              mpFDICxBKCLASSlog#,
               #mpFDICxBKCLASS2
               )

# equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)

modelplot(models[1:2]) +
  labs(title  = "Banks",
x = "Change in Log Odds of Commenting",
caption = "Reference Category = Commercial Bank") +
  theme(panel.grid.major.x =  element_blank(),
        panel.grid.major.y =  element_blank()) + 
  scale_color_viridis_d(end = .6)


save(models, rows,
     file = here::here("models", "CFPB", "mpFDIC2.Rdata"))
```


#### Predicted probabibility of commenting by bank type

```{r mp-FDIC2-predict, fig.height=2.5, fig.width=3.5}
 
 # A data frame of values at which to estimate probabilities:
values <- FDIC_resources %>% 
  #filter(org_type == "Bank") %>% 
  tidyr::expand(ASSETS_b = c(1,10,100,1000), # seq(0,100,20),
                Class2) %>% mutate(ASSETS_b2 = ASSETS_b^2)

predicted <- marginaleffects::predictions(mpFDICxBKCLASSlog,
                         newdata = values) 

names(predicted)


# As a plot
p <- predicted %>% 
  mutate(Class2 = str_replace(Class2, " ", "\n")) %>% 
  ggplot() + 
  aes(x = ASSETS_b, y = estimate, shape = Class2, color = Class2
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), 
                  alpha = .7,
                  position = position_dodge(width = .5) 
                  )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  #coord_flip() +
  labs(y = 'Probability of Commenting', 
       x = "Assets (Billions)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
  theme(#axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        #panel.grid.major.y = element_blank()
        )+
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma")  +
  scale_x_log10()

p 
```

### Non-profits

Assets in billions

```{r mp-nonprofits}
nonprofit_resources %<>% mutate(ASSETS_b = assets/1000000000)

mpNonprofit <- glm(commented ~ ASSETS_b,
           data = nonprofit_resources , 
             family=binomial(link="logit"))

mpNonprofit_revenue <- glm(commented ~ ASSETS_b + revenue,
           data = nonprofit_resources, 
             family=binomial(link="logit"))

mpNonprofit_ind_assoc <- glm(commented ~ ASSETS_b + revenue + ind_assoc,
           data = nonprofit_resources %>% mutate(ind_assoc = SUBSECTION == "06"), 
             family=binomial(link="logit"))

mpNonprofit_subsection <- glm(commented ~ ASSETS_b + revenue + SUBSECTION,
           data = nonprofit_resources, 
             family=binomial(link="logit"))

models <- list(mpNonprofit, mpNonprofit_revenue, mpNonprofit_ind_assoc)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Comment",
  `2` = "Comment",  
  `3` = "Comment" 
)

# equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)

modelplot(models)+ 
  theme(panel.grid.major.x =  element_blank()) + 
  labs(x = "Change in Log Odds of Commenting")
```

### Credit Unions

ASSETS_b in billions

 
```{r mp-credit-unions}
creditunions %<>% mutate(ASSETS_b = assets/1000000000)


mp_creditunions <- glm(commented ~ ASSETS_b,
           data = creditunions, 
             family=binomial(link="logit"))

models <- list(mp_creditunions)


rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Commented",
)

attr(rows, 'position') <- c(0)

# equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)

modelplot(models)+ 
  theme(panel.grid.major.x =  element_blank()) + 
  labs(x = "Change in Log Odds of Commenting per Billion in Assets")
```

### Banks, Non-profits, Credit Unions Compared

```{r mp-nonprofit-credit-unions}
# nonprofit-credit-unions
models <- list(mpFDICbillions, mpNonprofit, mp_creditunions)

names(models) <- c("Banks", "Non-profits", "Credit Unions")


modelplot(models) + 
  theme(panel.grid.major.x =  element_blank()) + 
  labs(x = "Change in Log Odds of Commenting per Billion in Assets") +
  facet_wrap("model", scales = "free", ncol = 1) +
  scale_color_viridis_d(option = "plasma", end = .7)


rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Commented",
  `2` = "Commented",
  `3` = "Commented"
)

attr(rows, 'position') <- c(0)

modelsummary(models)

save(models, rows, 
     file = here::here("models", "CFPB", "pr-of-comment.Rdata"))
```

### Campaign Donors

```{r mp-opensecrets-predict, fig.height=2.5, fig.width=2.5}
# TODO JOIN org_type2 and lobbying expend

opensecrets %<>% mutate(MeanContribAmount_t = MeanContribAmount/1000,
                        TotalContribAmount_t = TotalContribAmount/1000,
                        MeanContribAmount_m = MeanContribAmount/1000000,
                        TotalContribAmount_m = TotalContribAmount/1000000)

mpOpensecrets <- glm(commented ~ MeanContribAmount_t,
           data = opensecrets, 
             family=binomial(link="logit"))

mpOpensecrets_total <- glm(commented ~ TotalContribAmount_t,
           data = opensecrets, 
             family=binomial(link="logit"))


mpOpensecrets_log <- glm(commented ~ log(MeanContribAmount_t),
           data = opensecrets, 
             family=binomial(link="logit"))

mpOpensecrets_total_log <- glm(commented ~ log(TotalContribAmount_t),
           data = opensecrets, 
             family=binomial(link="logit"))

models <- list(mpOpensecrets, mpOpensecrets_total,
               mpOpensecrets_log, mpOpensecrets_total_log)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Commented",
  `2` = "Commented",
  `3` = "Commented",
  `4` = "Commented"
)

attr(rows, 'position') <- c(0)


# equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)

save(models, rows, file =  here::here("models", "CFPB", "mp-opensecrets.Rdata"))


# A data frame of values at which to estimate probabilities:
values <- opensecrets %>% 
  #filter(org_type == "Bank") %>% 
  tidyr::expand(MeanContribAmount_t = c(1,10,100) )#, org_type = "Bank") 

predicted <- marginaleffects::predictions(mpOpensecrets_log,
                         newdata = values) 

names(predicted)


# As a plot
p <- predicted %>% 
  ggplot() + 
  aes(x = MeanContribAmount_t, y = estimate#, shape = org_type, color = org_type
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), alpha = .7, position = position_dodge(width = 0.010) )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  #coord_flip() +
  labs(y = 'Probability of Commenting', 
       x = "PAC Contributions ($1,000s)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
  theme(#axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        #panel.grid.major.y = element_blank()
        )+
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma")  +
  scale_x_log10()

p 
```

### Lobbying

```{r mp-opensecrets-lobbying-predict, fig.height=2.5, fig.width=2.5}
# TODO JOIN org_type2 and lobbying expend

opensecrets %<>% mutate(MeanLobbyingAmount_t = MeanLobbyingAmount/1000,
                        TotalLobbyingAmount_t = TotalLobbyingAmount/1000,
                        MeanLobbyingAmount_m = MeanLobbyingAmount/1000000,
                        TotalLobbyingAmount_m = TotalLobbyingAmount/1000000)

mpOpensecrets <- glm(commented ~ MeanLobbyingAmount_t,
           data = opensecrets, 
             family=binomial(link="logit"))

mpOpensecrets_total <- glm(commented ~ TotalLobbyingAmount_t,
           data = opensecrets, 
             family=binomial(link="logit"))


mpOpensecrets_log <- glm(commented ~ log(MeanLobbyingAmount_t),
           data = opensecrets, 
             family=binomial(link="logit"))

mpOpensecrets_total_log <- glm(commented ~ log(TotalLobbyingAmount_t),
           data = opensecrets, 
             family=binomial(link="logit"))

models <- list(mpOpensecrets, mpOpensecrets_total,
               mpOpensecrets_log, mpOpensecrets_total_log)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Commented",
  `2` = "Commented",
  `3` = "Commented",
  `4` = "Commented"
)

attr(rows, 'position') <- c(0)


# equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)

save(models, file =  here::here("models", "CFPB", "mp-opensecrets-lobbying.Rdata"))

# A data frame of values at which to estimate probabilities:
values <- opensecrets %>% 
  #filter(org_type == "Bank") %>% 
  tidyr::expand(MeanLobbyingAmount_t = c(1,10,100) )#, org_type = "Bank") 

predicted <- marginaleffects::predictions(mpOpensecrets_log,
                         newdata = values) 

names(predicted)


# As a plot
p <- predicted %>% 
  ggplot() + 
  aes(x = MeanLobbyingAmount_t, y = estimate#, shape = org_type, color = org_type
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), alpha = .7, position = position_dodge(width = 0.010) )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  #coord_flip() +
  labs(y = 'Probability of Commenting', 
       x = "PAC Contributions ($1,000s)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
  theme(#axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        #panel.grid.major.y = element_blank()
        )+
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma")  +
  scale_x_log10()

p 
```

---

### By Market Cap

```{r mp-compustat}
compustat %<>% mutate(commented = Commented == "Commented",
                      marketcap_b = marketcap2/1000000000,
                      marketcap_b2 = marketcap_b^2)


mpCompustat <- glm(commented ~ marketcap_b,
           data = compustat, 
             family=binomial(link="logit"))

top_naics <- compustat %>% count(naics, sort = T) %>% 
  drop_na(naics) %>% 
  top_n(10, wt = n) %>% 
  pull(naics)

mpCompustat_naics <- glm(commented ~ NAICS_,
           data = compustat %>% mutate(NAICS_ = ifelse(naics %in% top_naics, naics, "other")), 
             family=binomial(link="logit"))

models <- list(mpCompustat, mpCompustat_naics)

# equatiomatic::extract_eq(models[[1]]) 

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Commented",
  `2` = "Commented"#,
  #`3` = "Commented"
)

modelsummary(models)


# new table wiothout NAICS 
mpCompustatlog <- glm(commented ~ log(marketcap_b),
           data = compustat, 
             family=binomial(link="logit"))

mpCompustat2 <- glm(commented ~ marketcap_b2,
           data = compustat, 
             family=binomial(link="logit"))






models <- list(mpCompustat, mpCompustatlog)#, mpCompustat2)

# equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)

#modelplot(models)

 modelplot(mpCompustat)
 
 # modelplot(mpCompustat_naics)

save(models, rows, file = here::here("models", "CFPB", "mpCompustat.Rdata"))
```

#### Predicted probabilites by market cap

```{r mp-compustat-predict, fig.height=2.5, fig.width=2}
 
 # A data frame of values at which to estimate probabilities:
values <- compustat %>% 
  #filter(org_type == "Bank") %>% 
  tidyr::expand(marketcap_b = c(1,10,100,1000) ) %>% 
  mutate(marketcap_b2 = marketcap_b^2)

predicted <- marginaleffects::predictions(mpCompustatlog,
                         newdata = values) 

names(predicted)


# As a plot
p <- predicted %>% 
  ggplot() + 
  aes(x = marketcap_b, y = estimate#, shape = org_type, color = org_type
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), 
                  alpha = .7,
                  position = position_dodge(width = 0.010) 
                  )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  #coord_flip() +
  labs(y = 'Probability of Commenting', 
       x = "Market Cap. (Billions)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
  theme(#axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        #panel.grid.major.y = element_blank()
        )+
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma") +
  scale_x_log10()

p 
```

## Together

```{r mp-all}
all <- full_join(
  FDIC_resources %>% 
    ungroup() %>% 
    dplyr::select(assets = ASSET, 
                  commented, 
                  org_type2 = Class) %>% 
    mutate(org_type = "Bank"),
  nonprofit_resources %>% 
    ungroup() %>% 
    dplyr::select(assets, commented, SUBSECTION) %>% 
    mutate(org_type = ifelse(SUBSECTION == "06",
                             "Industry assoc.",  
                             "Other non-profit") %>% replace_na("Other non-profit")) 
) %>% 
  full_join(
  creditunions %>% 
    ungroup() %>% 
    dplyr::select(assets, commented) %>% mutate(org_type = "Credit union")
  )

distinct(all, commented, org_type)

## ADD SECTIONS OF IRS CODE HERE

all %<>% mutate(assets_b = assets  / 100000000,
                assets_b2 = assets_b^2) # %>% filter(org_type != " SB", org_type != " SM")

mpAll <- glm(commented ~ assets_b + org_type,
           data = all, 
             family=binomial(link="logit"))

mpAlli <- glm(commented ~ assets_b * org_type,
           data = all, 
             family=binomial(link="logit"))

# # business assns split out from non-profits
# mpAlli_np_solo <- glm(commented ~ assets_b * org_type,
#            data = all %>% 
#              mutate(
#                org_type = ifelse(org_type == "Non-profit", c(paste(org_type, SUBSECTION)), org_type)
#              ) %>%
#              filter(SUBSECTION %in% c("03","06")), 
#              family=binomial(link="logit"))
# 
# # business assns split out from non-profits
# `%!in%` <- base::Negate(`%in%`)
# 
# mpAlli_all_np_subsection <- glm(commented ~ assets_b * org_type,
#            data = all,# %>% 
#              # filter(
#              #   !(org_type == "Non-profit" & SUBSECTION %!in% c("03","06"))
#              #   ) %>%
#              # mutate(
#              #   org_type = ifelse(org_type == "Non-profit", c(paste(org_type, SUBSECTION)), org_type),
#              # ),
#              family=binomial(link="logit"))


mpAlllog <- glm(commented ~ log(assets_b+1) + org_type,
           data = all, 
             family=binomial(link="logit"))

mpAllilog <- glm(commented ~ log(assets_b+1) * org_type,
           data = all, 
             family=binomial(link="logit"))

mpAllquad <- glm(commented ~ assets_b + assets_b2 + org_type,
           data = all, 
             family=binomial(link="logit"))

mpAlliquad <- glm(commented ~ assets_b * org_type + assets_b2 * org_type ,
           data = all, 
             family=binomial(link="logit"))


models <- list(mpAll, mpAlli,
               mpAlllog, mpAllilog#,
               #mpAllquad, mpAlliquad
               )

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Commented",
  `2` = "Commented",
    `3` = "Commented",
  `4` = "Commented"#,
 # `5` = "Commented",
 # `6` = "Commented"
)

attr(rows, 'position') <- c(0)

#equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)

# modelplot(models)

save(models, rows,
     file = here::here("models", "CFPB", "mpAll.Rdata"))
```


### Predicted Probability of commenting by Non-Profit Type

```{r mp-all-predict, fig.height=2.5, fig.width=3.5}
values <- all %>% 
  tidyr::expand(assets_b = seq(0,100,10), 
                org_type) %>% 
  mutate(assets_b2 = assets_b^2)


predicted <- marginaleffects::predictions(
  mpAll,
  newdata = values) 

p <- predicted %>% 
  ggplot() + 
  aes(x = assets_b, y = estimate, shape = org_type, color = org_type
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), alpha = .7, position = position_dodge(width = .5) )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  #coord_flip() +
  labs(y = 'Probability of Commenting', 
       x = "Assets (Billions)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
  theme(#axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        #panel.grid.major.y = element_blank()
        )+
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma")  

p


# 
# predicted <- marginaleffects::predictions(mpAlli_np_solo,
#                          newdata = values)
# p <- predicted %>%
#   ggplot() +
#   aes(x = assets_b*1000, y = estimate#, shape = org_type, color = org_type
#       ) +
#   geom_pointrange(aes(ymin = conf.low,
#                   ymax = conf.high), alpha = .7, position = position_dodge(width = 0.010) )  +
#   geom_hline(yintercept = 0, linetype = 2) +
#   #coord_flip() +
#   labs(y = 'Probability of Commenting',
#        x = "Assets (Millions)",
#        color = "",
#        shape = "",
#        title = "CFPB Only ") +
#   theme_minimal() +
#   theme(#axis.text.y = element_blank(),
#         #axis.ticks.y = element_blank(),
#         #panel.grid.major.y = element_blank()
#         )+
#     scale_color_viridis_d(begin = 0, end = .6, option = "plasma")
# 
# # predicted probability of commenting Bank, Credit Union, NP 3 and NP 6
# only_np <- p  +  aes(color = org_type) + labs(color = "")
# 
# ggsave(plot = only_np, filename = "figs/only-np-sep-mp-all-predict-quad-1.png", bg="white")
# 

```


###  Predicted probability of commenting by assets 

```{r}
# A data frame of values at which to estimate probabilities:
values <- all %>% 
  #filter(org_type == "Bank") %>% c(1,10,100)
  tidyr::expand(assets_b = seq(0,100,10), org_type) %>% 
  mutate(assets_b2 = assets_b^2)
```



### Base model with interactions (2) 

```{r,  mp-alli-predict, fig.height=2.5, fig.width=3.5}
predicted <- marginaleffects::predictions(mpAlli,
                         newdata = values) 

names(predicted)


# As a plot
p <- predicted %>% 
  ggplot() + 
  aes(x = assets_b, y = estimate, shape = org_type, color = org_type
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), alpha = .7, position = position_dodge(width = 0.010) )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  #coord_flip() +
  labs(y = 'Probability of Commenting', 
       x = "Assets (Billions)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
  theme(#axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        #panel.grid.major.y = element_blank()
        )+
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma")  

p  +  aes(color = org_type) + labs(color = "")


# p +   facet_wrap("org_type", ncol = 1) #+ ylim(0,.5) 
```

```{r,  mp-all-predict-faceted, fig.height=2.5, fig.width=5.5}
p +  facet_wrap("org_type", ncol = 2, scales = "free") +  aes(color = org_type) + labs(color = "") # + ylim(0,.5) 
```



### Log model with interactions (2) 

```{r}
# A data frame of values at which to estimate probabilities:
values <- all %>% 
  tidyr::expand(assets_b = c(.1, 1,10,100), org_type) %>% 
  mutate(assets_b2 = assets_b^2)
```

```{r,  mp-all-predict-log, fig.height=2.5, fig.width=3.5}
predicted <- marginaleffects::predictions(mpAllilog,
                         newdata = values)

# As a plot
p <- predicted %>% 
  ggplot() + 
  aes(x = assets_b, y = estimate, shape = org_type, color = org_type
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), alpha = .7, position = position_dodge(width = 0.5) )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  labs(y = 'Probability of Commenting', 
       x = "Assets (Billions)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma")  +
  scale_x_log10()

p + aes(color = org_type) + labs(color = "")  
```

### Quadratic model with interactions (6) 

```{r,  mp-all-predict-quad, fig.height=2.5, fig.width=3.5}
predicted <- marginaleffects::predictions(mpAlliquad,
                         newdata = values) # %>%  filter(org_type != "Industry assoc.")


# As a plot
p <- predicted %>% 
  ggplot() + 
  aes(x = assets_b, y = estimate, shape = org_type, color = org_type
      ) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), alpha = .7, position = position_dodge(width = 0.50) )  + 
  geom_hline(yintercept = 0, linetype = 2) +
  #coord_flip() +
  labs(y = 'Probability of Commenting', 
       x = "Assets (Billions)",
       color = "",
       shape = "", 
       title = "CFPB Only ") + 
  theme_minimal() + 
  theme()+
    scale_color_viridis_d(begin = 0, end = .6, option = "plasma")  +
  scale_x_log10()

#p+ aes(color = org_type) + labs(color = "") 
```

```{r mp-all-predict-blank, fig.height=2.5, fig.width=3}
p$layers[1] <- NULL +   facet_wrap("org_type", ncol = 1) 


p  + ylim(0,1) 
```

# TODO 

Priorities for matching that will give us the most leverage:

- [ ] Best match in *each* dataset rather than best match in *one* dataset: https://finreggroup.slack.com/archives/C027MRLQFLJ/p1650733175102459

- [ ] Comments on dockets with 0 comments matched: https://judgelord.github.io/finreg/participation#Asset_data

- [ ] Underpowered subsets, especially marketcap (hopefully matching both compustat and CIK will help with this): https://judgelord.github.io/finreg/participation#By_Market_Cap

- [ ] FDIC `BKCLASS` == "national associations" that we are currently dropping: https://judgelord.github.io/finreg/participation#FDIC_instituttions  https://finreggroup.slack.com/archives/C027MRLQFLJ/p1653322086231879

- [ ] False positives that I am currently dropping https://finreggroup.slack.com/archives/C027MRLQFLJ/p1650658969445029

Analyses to clean up and add to the paper 

- [ ] Lobbying expenditures from CRP (replication of all PAC figures and models)

- [ ] Non-profit revenue (maybe just add the revenue figures and models to the appendix)

- [ ] the full (best-ish) model includes nonprofits, credit unions, and each type of bank as separate org_types. This model is run above but needs to be investigated 

Presentation 

- [ ] Predicted probability plots for all models presented in the paper. These should replace all tables. All tables should appear in the appendix. 

- [ ] Non-profit and credit union plots for the correlation between assets and sophistication
