---
title: "Representation in FRS Rulemaking"
#subtitle: "Appendix and Replication Code"
output:
    bookdown::html_document2:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
      number_sections: false
---

```{r options, include=FALSE}
source(here::here("code", "setup.R"))

## Change defaults for R chunks
knitr::opts_chunk$set(cache = FALSE,
                      fig.path = "figs/",
                      #fig.retina = 3, #6, #FIXME for publication-quality images 
                      fig.height = 3,
                      fig.width = 6)
```


## Assets 

- see https://judgelord.github.io/finreg/participation

- Nonprofit `assets` and `revenue` from 990 data from https://www.irs.gov/charities-non-profits/form-990-series-downloads: `finreg/data/nonprofit_resources.Rdata` or `finreg/data/merged_resources/nonprofit_resources.csv`

```{r asset-data}
#FIXME retain EIN in rdata 
# load(here("data", "nonprofit_resources.Rdata"))
nonprofit_resources <- read_csv(here::here("data", "merged_resources/nonprofits_resources.csv")) 

# ALL OTHER ASSET DATA 
load(here::here("data", "commenter_assets.Rdata"))

d <- commenter_assets |>
  filter(comment_agency == "FRS") 

#FIXME MOVE TO TOP 
d$comment_url %<>% str_replace("document\\?D=", "comment/")
```


## Employees and Volunteers 

From 2015 IRS 990 

```{r irs}
irs <- read_csv(here::here("data", "irs_990_xmls_2015.csv")) %>% 
  mutate(ein = as.numeric(EIN))

irs %<>% distinct(ein, TotalVolunteersCnt, TotalEmployeeCnt, WebsiteAddressTxt) 

irs %<>% group_by(ein) %>% arrange(-TotalEmployeeCnt) %>% arrange(-TotalVolunteersCnt) %>% slice_head(n = 1) %>% ungroup() 

# irs %>%  count(EIN, TotalEmployeeCnt, TotalVolunteersCnt) %>% arrange(-n)

```

### All nonprofits
```{r}
nonprofit_resources %<>% full_join(irs) %>% 
  mutate(commented = ein %in% commenter_assets$`nonprofits_resources-bestMatch:ein`,
         Commented = ifelse(commented, "Commenter", "Non-commenter")) %>% 
  filter(assets > 10)

nonprofit_resources  %>% 
  select(WebsiteAddressTxt, TotalVolunteersCnt, TotalEmployeeCnt, commented) %>%  arrange(-TotalVolunteersCnt) %>% kablebox()
```


### Nonprofits that commented on a Dodd-Frank rule
```{r}
nonprofit_resources %>% filter(commented) %>% 
  select(WebsiteAddressTxt, TotalVolunteersCnt, TotalEmployeeCnt, commented) %>%  arrange(-TotalVolunteersCnt) %>% kablebox()
```


### Employees x Volunteers 
```{r employee-vol}
nonprofit_resources %>% 
  ggplot() + 
  aes(x = log(TotalEmployeeCnt), y = log(TotalVolunteersCnt), color = commented) + 
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", color = "grey") + 
  geom_smooth(color = "black") + 
  facet_wrap("Commented") +
  theme(legend.position = "none") +
  labs(x = "Log(Employees)",
       y = "Log(Volunteers)",
       title = "Volunteers by Employees of Nonprofits\nthat Did and Did Not Comment on a FRS Rule")
```


### Assets x Volunteers 
```{r assets-vol}
nonprofit_resources %>% 
  ggplot() + 
  aes(x = log(assets), y = log(TotalVolunteersCnt), color = commented) + 
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", color = "grey") + 
  geom_smooth(color = "black") + 
  facet_wrap("Commented") +
  theme(legend.position = "none") +
  labs(x = "Log(Assets)",
       y = "Log(Volunteers)",
       title = "Volunteers by Assets of Nonprofits\nthat Did and Did Not Comment on a FRS Rule")
```


# Probability of commenting, controlling for the number of volunteers

Model 1 includes all nonprofits with asset data 

Models 2-5 subset to nonprofits with volunteer data

```{r mp-nonprofits-vol}
nonprofit_resources %<>% mutate(Assets = assets/1000000000,
                                log_assets = log(assets +1))

mpNonprofit <- glm(commented ~ Assets,
           data = nonprofit_resources , 
             family=binomial(link="logit"))

mpNonprofit_v <- glm(commented ~ Assets,
           data = nonprofit_resources %>% filter(!is.na(TotalVolunteersCnt)), 
             family=binomial(link="logit"))

mpNonprofit_vol <- glm(commented ~ Assets + TotalVolunteersCnt,
           data = nonprofit_resources, 
             family=binomial(link="logit"))

mpNonprofit_vol_log <- glm(commented ~ Assets + log(TotalVolunteersCnt + 1),
           data = nonprofit_resources, 
             family=binomial(link="logit"))

mpNonprofit_vol_log_log <- glm(commented ~ log(assets + 1) + log(TotalVolunteersCnt + 1),
           data = nonprofit_resources, 
             family=binomial(link="logit"))

models <- list(mpNonprofit, 
               mpNonprofit_v,
               mpNonprofit_vol_log_log,
               mpNonprofit_vol,
               mpNonprofit_vol_log)

rows <- tibble(
  term = c("Dependent Variable"),
  `1` = "Comment",
  `2` = "Comment",  
  `3` = "Comment",  
  `4` = "Comment",  
  `5` = "Comment"
)

#equatiomatic::extract_eq(models[[1]]) 

modelsummary(models)
```
