---
title: "Validating FinReg Comment Data"
#subtitle: "Appendix and Replication Code" 
output:
    bookdown::html_document2:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
      number_sections: false
# output:
#   xaringan::moon_reader:
#     lib_dir: libs
#     mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-AMS_HTML"
#     css: xaringan-themer.css
#     nature:
#       highlightStyle: github
#       highlightLines: true
#       countIncrementalSlides: false
---



```{r options, include=FALSE}
# rmarkdown::render("docs/participation.Rmd")

## Sets defaults for R chunks
knitr::opts_chunk$set(#echo = FALSE, # echo = TRUE means that code will show
                      cache = FALSE,
                      #cache = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.show="hold",
                      fig.pos= "htbp",
                      fig.path = "../figs/",
                      fig.align='center',
                      fig.cap = '   ',
                      fig.retina = 6,
                      fig.height = 3,
                      fig.width = 7,
                      out.width = "100%",
                      out.extra = "")

library("xaringan")
library("xaringanthemer")
library("here")


style_mono_light(base_color = "#3b444b",
          link_color = "#B7E4CF",
          #background_color = "#FAF0E6", # linen
          header_font_google = google_font("PT Sans"), 
          text_font_google = google_font("Old Standard"), 
          text_font_size = "18px",
          padding = "10px",
          code_font_google = google_font("Inconsolata"), 
          code_inline_background_color    = "#F5F5F5", 
          table_row_even_background_color = "#ddede5",
          extra_css = 
            list(".remark-slide-number" = list("display" = "none")))
```

```{r setup}
options(scipen=999)

source(here::here("code", "setup.R"))

# defaults for plots
library(ggplot2); theme_set(theme_minimal());
options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_color_discrete <- function(...){
  scale_color_viridis_d(..., direction = -1, 
                        begin = 0, end = .9, option = "plasma")}
scale_fill_discrete <- function(...){
  scale_fill_viridis_d(..., direction = -1, 
                       begin = 0, end = .9, option = "plasma")}

scale_color_continuous <- function(...){
  scale_color_viridis_c(..., direction = -1, 
                        option = "plasma")}
scale_fill_continuous <- function(...){
  scale_fill_viridis_c(..., direction = -1, 
                       option = "plasma")}
```

# Data

This document uses the same data we use to generate our tables and figures: https://judgelord.github.io/finreg/participation#Save_data

```{r data}
load( here::here("data", "commenter_assets.Rdata"))

commenter_assets %<>% mutate(document_id = comment_url %>% str_extract("CFPB.*"))
```

The [validation data](https://github.com/judgelord/finreg/blob/main/data/validation.csv) includes hand-coded comments on the CFPB payday loan and debt collection rules.
```{r data-validation}
#FIXME move to another script and save CFPB comment to make this replicate
load(here::here("data", "comments_coded.Rdata") %>% str_replace("finreg", "dissertation")) 

# FIXME Correction to some elected comments miscoded as org comments 
comments_coded %<>% mutate(
  comment_type = ifelse(
    str_dct(org_type, "assembly|house|senate|governor"),
    "elected",
    comment_type))

# comments_coded %>% filter(comment_type == "org") %>% distinct(org_type %>% str_remove(";.*"), comment_type)


d <- comments_coded %>% 
  #select dockets in Dodd-Frank data 
  filter(docket_id %in% commenter_assets$docket_id) %>%
  # join in Dodd-Frank data
  full_join(commenter_assets,
            by = c("docket_id", "document_id"),
            suffix = c("_hand", "_auto")) %>% 
  # indicator
  mutate(asset_data = ifelse(is.na(org_name_auto),
                             "no asset data",
                             "asset data"))

concat <- . %>% unique() %>% str_c(collapse = "\n")

# extract orgs for hand coding
orgs <- d %>% add_count(org_name_auto, name = "comment_count") %>%
  group_by(org_name_auto) %>% 
  mutate(across(everything(), concat)) %>% distinct()

orgs %<>% select(comment_title,
             ends_with("_auto"),
             comment_type_hand = comment_type,
             ends_with("_hand"),
             starts_with("org_"),
             assets,
             revenue,
             starts_with("comment_"))  %>%
  select(-starts_with("comment_txt"),
         -comment_url_hand,
         -org_lead)

replace_na_strings <- . %>% replace_na("")

orgs %>% #arrange(-org_resources) %>%
  mutate(across(everything(), replace_na_strings)) %>% mutate(comment_count = comment_count %>% as.numeric())  %>% write_csv(file = here("data","finreg_orgs_to_code.csv"))

```

```{r, eval=FALSE}
library(googlesheets4)
ss <- gs4_get("1AYWnfp3DK99FGS4hncQEvw4lUWgK0iwb-xHWOYx_uew") 
1

sheet_write(orgs %>% 
              mutate(comment_count = comment_count %>% as.numeric()) %>%  
              filter(comment_count < 1000), ss, sheet = str_c("finreg_orgs_to_code", Sys.Date() )

```

```{r}
# filter to hand-coded cases
d %<>% drop_na(comment_type)

d %>% distinct(docket_id) %>% kable()

d %>% select(comment_title,
             ends_with("_auto"),
             comment_type_hand = comment_type,
             ends_with("_hand"),
             coalition_hand = coalition,
             comment_url) %>%
  kablebox()

d %>% select(comment_title,
             ends_with("auto"),
             comment_type_hand = comment_type,
             ends_with("_hand"),
             coalition_hand = coalition,
             comment_url) %>%
  write_csv(here("data", "validation.csv"))
```

---

# Validation

## Of `r nrow(d)` hand-coded comments on these rules, `r nrow(d %>% filter(asset_data == "asset data"))` are currently matched with asset data. 

Of the `r nrow(d %>% filter(comment_type == "org"))` comments hand-coded as sophisticated comments from an organization (excluding mass comments, individuals, or comments from elected officials), `r nrow(d %>% filter(comment_type == "org", asset_data == "asset data"))` are currently matched with asset data. 

## Asset data completeness by hand-coded org type

(high-level org type coding only)

```{r validation, fig.width=4, out.width="50%"}
# drop org type details, focus on main catagories
d %<>% 
  mutate(subtype = org_type_hand %>% 
           str_remove("[A-z]*;") %>%
           str_remove(";.*"),
         org_type_hand = org_type_hand %>%
           str_remove(";.*") %>% 
           str_remove("s$")
         )

# overall
d %>% 
  filter(comment_type == "org") %>%
  ggplot() +
  aes(x = asset_data, 
      fill = org_type_hand) + 
  coord_flip() + 
  geom_bar()+ 
  labs(x = "",
       y = "")


d %>% 
  filter(comment_type == "org") %>%
  ggplot() +
  aes(x = org_type_auto, 
      fill = org_type_hand) + 
  geom_bar() + 
  coord_flip() + 
  labs(x = "Data Source",
       y = "")
```

```{r validation-type, fig.height=5, out.width="90%"}

d %>% 
  filter(comment_type == "org",
         org_type_hand == "ngo") %>%
  mutate(org_type_auto = org_type_auto %>% replace_na(" no asset data")) %>% 
  ggplot() +
  aes(x = subtype, 
      fill = org_type_auto) + 
  geom_bar() + 
  coord_flip() + 
  labs(title = "NGOs",
       x = "",
       fill = "Data Source",
       y = "Hand-coded ngo subtypes")+ 
  scale_fill_viridis_d()

d %>% 
  filter(comment_type == "org",
         org_type_hand == "corp") %>%
  mutate(org_type_auto = org_type_auto %>% replace_na(" no asset data")) %>% 
  ggplot() +
  aes(x = subtype, 
      fill = org_type_auto) + 
  geom_bar() + 
  coord_flip() + 
  labs(title = "Corps",
       x = "",
       fill = "Data Source",
       y = "Hand-coded corp subtypes")+ 
  scale_fill_viridis_d()

d %>% 
  filter(comment_type == "org",
         org_type_hand == "corp group") %>%
  mutate(org_type_auto = org_type_auto %>% replace_na(" no asset data")) %>% 
  ggplot() +
  aes(x = subtype, 
      fill = org_type_auto) + 
  geom_bar() + 
  coord_flip() + 
  labs(title = "Corp groups (business associations)",
       x = "",
       fill = "Data Source",
       y = "Hand-coded corp group subtypes")+ 
  scale_fill_viridis_d()

d %>% 
  filter(comment_type == "org",
         org_type_hand == "gov") %>%
  mutate(org_type_auto = org_type_auto %>% replace_na(" no asset data")) %>% 
  ggplot() +
  aes(x = subtype, 
      fill = org_type_auto) + 
  geom_bar() + 
  coord_flip() + 
  labs(title = "Governments (should not have asset data?)",
       x = "",
       fill = "Data Source",
       y = "Hand-coded government subtypes")+ 
  scale_fill_viridis_d()
```

We are capturing credit unions fairly well and seem to be capturing a high percentage of unions, think tanks, philanthropy, legal, and financial services NGOs. 

We are undercounting corporations, especially law firms and, surprisingly, banks (these are probably small banks).

## By hand-coaded "coalition"

*A few of these "coalitions" include organizations lobbying alone, without coalition partners. 

```{r validation-by-coalition, fig.width=10, fig.height=7}
d %>% 
  filter(comment_type == "org") %>%
  ggplot() +
  aes(x = asset_data, 
      fill = org_type_hand) + 
  geom_bar() + 
  coord_flip() + 
  facet_wrap(#scales = "free_y",
             "coalition") +
  theme_bw() +
  theme(strip.text = element_text(hjust = 0)) + 
  labs(x = "",
       y = "") 

```

---

By hand-coded coalition type

```{r validation-by-coalition-type, fig.width=5, fig.height=2, out.width= "70%"}
d %>% 
  filter(comment_type == "org") %>%
  ggplot() +
  aes(x = asset_data, 
      fill = org_type_hand) + 
  geom_bar() + 
  coord_flip() + 
  facet_wrap(#scales = "free_y",
             "coalition_type") +
  theme_bw() +
  theme(strip.text = element_text(hjust = 0)) + 
  labs(x = "",
       y = "")

```


We are capturing almost none of the businesses that are lobbying public interest coalitions (many of these are small law firms). For example, we are not capturing the businesses that lobby alongside the ABA or the Center for Responsible Lending.


## Lobbying success by assets of coalition members

```{r validation-success}
d %>% 
  ggplot(  ) + 
  aes(y = coalition_success, x = assets,
      label = coalition) + 
  geom_jitter(alpha = .3, aes(size = coalition_size) ) + 
  geom_text(color = "blue") + 
  geom_smooth()

d %>% 
  ggplot(  ) + 
  aes(y = coalition_success, x = revenue,
      label = coalition) + 
  geom_jitter(alpha = .3, aes(size = coalition_size) ) + 
  geom_text(color = "blue") + 
  geom_smooth()
```


#TODO

- [ ] Validate efficacy against hand-coded success 
