---
title: "Validating FinReg Comment Data"
#subtitle: "Appendix and Replication Code" 
output:
    bookdown::html_document2:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
      number_sections: false
# output:
#   xaringan::moon_reader:
#     lib_dir: libs
#     mathjax: "https://cdn.bootcss.com/mathjax/2.7.1/MathJax.js?config=TeX-AMS_HTML"
#     css: xaringan-themer.css
#     nature:
#       highlightStyle: github
#       highlightLines: true
#       countIncrementalSlides: false
---



```{r options, include=FALSE}
# rmarkdown::render("docs/participation.Rmd")

## Sets defaults for R chunks
knitr::opts_chunk$set(#echo = FALSE, # echo = TRUE means that code will show
                      cache = FALSE,
                      #cache = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.show="hold",
                      fig.pos= "htbp",
                      fig.path = "../figs/",
                      fig.align='center',
                      fig.cap = '   ',
                      fig.retina = 6,
                      fig.height = 3,
                      fig.width = 7,
                      out.width = "100%",
                      out.extra = "")

library("xaringan")
library("xaringanthemer")
library("here")


style_mono_light(base_color = "#3b444b",
          link_color = "#B7E4CF",
          #background_color = "#FAF0E6", # linen
          header_font_google = google_font("PT Sans"), 
          text_font_google = google_font("Old Standard"), 
          text_font_size = "18px",
          padding = "10px",
          code_font_google = google_font("Inconsolata"), 
          code_inline_background_color    = "#F5F5F5", 
          table_row_even_background_color = "#ddede5",
          extra_css = 
            list(".remark-slide-number" = list("display" = "none")))
```

```{r setup}
options(scipen=999)

source(here::here("code", "setup.R"))

# defaults for plots
library(ggplot2); theme_set(theme_minimal());
options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_color_discrete <- function(...){
  scale_color_viridis_d(..., direction = -1, 
                        begin = 0, end = .9, option = "plasma")}
scale_fill_discrete <- function(...){
  scale_fill_viridis_d(..., direction = -1, 
                       begin = 0, end = .9, option = "plasma")}

scale_color_continuous <- function(...){
  scale_color_viridis_c(..., direction = -1, 
                        option = "plasma")}
scale_fill_continuous <- function(...){
  scale_fill_viridis_c(..., direction = -1, 
                       option = "plasma")}
```

# Data

This document uses the same data we use to generate our tables and figures: https://judgelord.github.io/finreg/participation#Save_data

```{r data}
load( here::here("data", "commenter_assets.Rdata"))

commenter_assets %<>% mutate(document_id = comment_url %>% str_extract("CFPB.*")) %>% select(-comment_url)
```

The validation set includes hand-coded comments on the CFPB payday loan and debt collection rules.
```{r data-validation}
#FIXME move to another script and save CFPB comment to make this replicate
load(here::here("data", "comments_coded.Rdata") %>% str_replace("finreg", "dissertation")) 

# FIXME Correction to some elected comments miscoded as org comments 
comments_coded %<>% mutate(
  comment_type = ifelse(
    str_dct(org_type, "assembly|house|senate|governor"),
    "elected",
    comment_type))

# comments_coded %>% filter(comment_type == "org") %>% distinct(org_type %>% str_remove(";.*"), comment_type)


d <- comments_coded %>% 
  #select dockets in Dodd-Frank data 
  filter(docket_id %in% commenter_assets$docket_id) %>%
  # join in Dodd-Frank data
  left_join(commenter_assets,
            by = c("docket_id", "document_id"),
            suffix = c("_hand", "_auto")) %>% 
  # indicator
  mutate(asset_data = ifelse(is.na(org_name_auto),
                             "no asset data",
                             "asset data"))

d %>% distinct(docket_id) %>% kable()


d %>% select(comment_title,
             ends_with("auto"),
             comment_type_hand = comment_type,
             ends_with("_hand"),
             coalition_hand = coalition,
             comment_url) %>%
  kablebox()
```

---

# Validation

Of `r nrow(d)` hand-coded comments on these rules, `r nrow(d %>% filter(asset_data == "asset data"))` are currently matched with asset data. Of the `r nrow(d %>% filter(comment_type == "org"))` comments hand-coded as sophisticated comments from an organization (excluding mass comments, individuals, or comments from elected officials), `r nrow(d %>% filter(comment_type == "org", asset_data == "asset data"))` are currently matched with asset data. 

## Asset data completeness by hand-coded org type

(high-level org type coding only)

```{r validation, fig.width=4, out.width="50%"}
# drop org type details, focus on main catagories
d %<>% 
  mutate(org_type_hand = org_type_hand %>%
           str_remove(";.*") %>% 
           str_remove("s$")
         )

# overall
d %>% 
  filter(comment_type == "org") %>%
  ggplot() +
  aes(x = asset_data, 
      fill = org_type_hand) + 
  coord_flip() + 
  geom_bar()+ 
  labs(x = "",
       y = "")


d %>% 
  filter(comment_type == "org") %>%
  ggplot() +
  aes(x = org_type_auto, 
      fill = org_type_hand) + 
  geom_bar() + 
  coord_flip() + 
  labs(x = "",
       y = "Data Source")
```


## By hand-coaded "coalition"

*A few of these "coalitions" include organizations lobbying alone, without coalition partners. 

```{r validation-by-coalition, fig.width=10, fig.height=7}
d %>% 
  filter(comment_type == "org") %>%
  ggplot() +
  aes(x = asset_data, 
      fill = org_type_hand) + 
  geom_bar() + 
  coord_flip() + 
  facet_wrap(#scales = "free_y",
             "coalition") +
  theme_bw() +
  theme(strip.text = element_text(hjust = 0)) + 
  labs(x = "",
       y = "")

```
